Summary of the things that I learned

### 2024-11-27 200-category-theory.tex
Fix a mistake about whether R tilde is a setcategory

\begin{remark}
  We will also briefly study the identity types of $ \tilde \C $. Take $ P = (F_1, X_1, r_1, s_1) $ and $ Q = (F_2, X_2, r_2, s_2) $ as objects of $ \tilde \C $. The identity type $ P = Q $ is equivalent to
  \[ \prod_{f : F_1 = F_2} \prod_{g: X_1 = X_2} r_1 \cdot \mathrm{idtoiso}(f) = \yo(\mathrm{idtoiso}(g)) \cdot r_2 \land s_1 \cdot \yo(\mathrm{idtoiso}(g)) = \mathrm{idtoiso}(f) \cdot s_2. \]
  \begin{center}
    \begin{tikzcd}
      F_1 \arrow[d, "\mathrm{idtoiso}(f)"'] \arrow[r, "s_1", shift left] & \yo(X_1) \arrow[d, "\yo(\mathrm{idtoiso}(g))"] \arrow[l, "r_1", shift left] \\
      F_2 \arrow[r, "s_2", shift left] & \yo(X_2) \arrow[l, "r_2", shift left]
    \end{tikzcd}
  \end{center}
  Since $ P \C $ is univalent,
  \[ f = \mathrm{isotoid}(\mathrm{idtoiso}(f)) = \mathrm{isotoid}(s_1 \cdot \yo(\mathrm{idtoiso}(g)) \cdot r_2). \]
  Since morphisms in $ \C $ form a set, the identities on the $ r_i $ and $ s_i $ are mere propositions, and the only `structure' of the identity type is the equality $ X_1 = X_2 $. Therefore, if $ \C $ is a setcategory, $ \tilde \C $ is a setcategory as well.

  Since $ \tilde \C $ has the same isomorphisms as $ \bar \C $, $ \tilde \C_M $ is not univalent for $ M $ as in the remark above.
\end{remark}

>>>>

We will also briefly study the identity types of $ \tilde \C $.
\begin{lemma}\label{lem:isaset-karoubi'}
  If $ \C $ is a setcategory, $ \tilde \C $ is a setcategory as well.
\end{lemma}
\begin{proof}
  Take $ P = (F_1, X_1, r_1, s_1) $ and $ Q = (F_2, X_2, r_2, s_2) $ as objects of $ \tilde \C $. The identity type $ P = Q $ is equivalent to
  \[ \prod_{f : F_1 = F_2} \prod_{g: X_1 = X_2} r_1 \cdot \mathrm{idtoiso}(f) = \yo(\mathrm{idtoiso}(g)) \cdot r_2 \land s_1 \cdot \yo(\mathrm{idtoiso}(g)) = \mathrm{idtoiso}(f) \cdot s_2. \]
  \begin{center}
    \begin{tikzcd}
      F_1 \arrow[d, "\mathrm{idtoiso}(f)"'] \arrow[r, "s_1", shift left] & \yo(X_1) \arrow[d, "\yo(\mathrm{idtoiso}(g))"] \arrow[l, "r_1", shift left] \\
      F_2 \arrow[r, "s_2", shift left] & \yo(X_2) \arrow[l, "r_2", shift left]
    \end{tikzcd}
  \end{center}
  Since $ P \C $ is univalent,
  \[ f = \mathrm{isotoid}(\mathrm{idtoiso}(f)) = \mathrm{isotoid}(s_1 \cdot \yo(\mathrm{idtoiso}(g)) \cdot r_2). \]
  Since morphisms in $ \C $ form a set, the identities on the $ r_i $ and $ s_i $ are mere propositions, and the only `structure' of the identity type is the equality $ X_1 = X_2 $. Therefore, if $ \C $ is a setcategory, $ \tilde \C $ is a setcategory as well.
\end{proof}
Since $ \tilde \C $ has the same isomorphisms as $ \bar \C $, $ \tilde \C_M $ is not univalent for $ M $ as in Remark \ref{rem:karoubi-not-univalent}.

### 2024-11-27 600-paper.tex
Fix a mistake about whether R tilde is a setcategory

  Therefore, this only works in $ \hat \R \simeq \hat C_{L_0} $. Suppose that we tried to do this in $ \tilde C_{L_0} $. Note that this category is equivalent to the category with as objects $ X : \Pshf L $, together with some $ (r, s) : X \triangleleft L $. Trying to define the pullback functor would already cause problems. To define a pullback, we would need to explicitly construct some retraction $ g^* Y \triangleleft L $, for which we would need a retraction $ Z \triangleleft L $. However, we have only mere existence of this retraction, so we would only be able to show mere existence of pullbacks, like in Taylor's proof. In Taylor's case, we were able to use the axiom of choice because the objects of $ \R $ form a set. However, the objects of $ \tilde \R $ do not form a set, and so we cannot use the axiom of choice here (Lemma 3.8.5 in \autocite{hottbook} shows why the axiom of choice only works for sets).

  Since we have an adjoint equivalence between $ \tilde C_{L_0} $ and $ \overline C_{L_0} = \R $, and since any reasoning about $ \R $ using presheaves would use this equivalence, we would run into the same problems if we tried try to apply Hyland's approach to $ \R $. However, note that there we might be able to use the axiom of choice to show mere existence of a pullback functor, like in Taylor's proof.
\end{remark}

>>>>

  Therefore, this only works in $ \hat \R \simeq \hat C_{L_0} $. Suppose that we tried to do this in $ \tilde \R = \tilde C_{L_0} $. Note that this category is equivalent to the category with as objects $ X : \Pshf L $, together with some $ (r, s) : X \triangleleft L $. Trying to define the pullback functor would already cause problems. To define a pullback, we would need to explicitly construct some retraction $ g^* Y \triangleleft L $, for which we would need a retraction $ Z \triangleleft L $. However, we have only mere existence of the latter, so we would only be able to show mere existence of pullbacks, like in Taylor's proof. For $ \R $, we would be able to use the adjoint equivalence between $ \R $ and $ \tilde \R $ to apply Hyland's reasoning with presheaves to $ \R $. Since $ C_{L_0} $ is a setcategory, $ \R $ and $ \tilde \R $ are also setcategories (Lemma \ref{lem:isaset-karoubi'}), so we can use the axiom of choice to show the existence of a pullback functor. However, this approach still gives only mere existence.
\end{remark}
